Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2025-05-12 autovi_paper.qmd
Provide brief desc for each module

The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments. Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes. The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs. These modules are discussed in detail in the package documentation.

>>>>

The package takes regression models and a `Keras` model as primary inputs. Modules for VSS prediction and $p$-value computation are fixed but accessible via function arguments, using `TensorFlow` for inference and statistical testing. The image loading module is also fixed, using `PIL` to read and resize images based on the `Keras` model’s input shape. The remaining seven modules are overridable, allowing users to adapt the workflow as needed. The data extraction module extracts a `data.frame` containing variables used in the regression model. The bootstrapping and refitting module resamples the data and refits the model. The fitted values and residuals extraction module returns these values as a `data.frame`. The auxiliary computation module calculates scagnostics such as monotonicity. The plotting module generates a `ggplot` in a standard format, and the plot saving module exports it at the same resolution as the training images. These modules are described in detail in the package documentation.

### 2025-05-12 autovi_paper.tex
Provide brief desc for each module

The modules for VSS prediction and \(p\)-value computation are
predefined and cannot be overridden, although users can interact with
them directly through function arguments. Similarly, the image reading
and resizing module is fixed but will adapt to different Keras models by
checking their input shapes. The remaining seven modules are designed to
be overridable, enabling users to tailor the infrastructure to their
specific needs. These modules are discussed in detail in the package
documentation.

>>>>

The package takes regression models and a \texttt{Keras} model as
primary inputs. Modules for VSS prediction and \(p\)-value computation
are fixed but accessible via function arguments, using
\texttt{TensorFlow} for inference and statistical testing. The image
loading module is also fixed, using \texttt{PIL} to read and resize
images based on the \texttt{Keras} model's input shape. The remaining
seven modules are overridable, allowing users to adapt the workflow as
needed. The data extraction module extracts a \texttt{data.frame}
containing variables used in the regression model. The bootstrapping and
refitting module resamples the data and refits the model. The fitted
values and residuals extraction module returns these values as a
\texttt{data.frame}. The auxiliary computation module calculates
scagnostics such as monotonicity. The plotting module generates a
\texttt{ggplot} in a standard format, and the plot saving module exports
it at the same resolution as the training images. These modules are
described in detail in the package documentation.
